Hydra Battles and Cie

### 2021-07-01 doc/hydras.tex
minor corrections

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, \'Evelyne Contejean,  Florian Hatat,  David Ilcinkas, 
Pascal Manoury,  Karl Palmskog, Sylvain Salvati, Alan Schmitt and Théo Zimmermann for their help on the elaboration of this document, and to the
 members of the \emph{Formal Methods} team and the \emph{Coq working group} at laBRI for their helpful comments 
on  oral presentations of this work.

>>>>

\section{Acknowledgements}
\label{sec:orgheadline5}
    Many thanks to Yves Bertot, \'Evelyne Contejean, Jéremy Damour,   Florian Hatat,  David Ilcinkas, 
Pascal Manoury,  Karl Palmskog, Sylvain Salvati, Alan Schmitt and Théo Zimmermann for their help on the elaboration of thislibrary and  document, and to the
 members of the \emph{Formal Methods} team and the \emph{Coq working group} at laBRI for their helpful comments 
on  oral presentations of this work.
